---
title: "San Juan Ostuncalco home census"
author: "Oscar"
date: "August 7, 2017"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
# Load used packages
library(package = "sf")
library(package = "leaflet")
library(package = "tidyverse")

# Configure document knitting
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r read-shapefiles}
sjo_perimeter <- read_sf("data/shapefiles/sjo_perimeter.shp")
sjo_blocks <- read_sf("data/shapefiles/sjo_blocks.shp")
```


## Study area

The following interactive map shows in yellow the study area selected in San
Juan Ostuncalto, and in blue the blocks included in the selected area
(internet required to present other map elements as roads and labels).

```{r plot-blocks}
leaflet() %>%
  addTiles() %>%
  addPolygons(data = sjo_perimeter, color = "yellow") %>%
  addPolygons(data = sjo_blocks, color = "blue")
```


# Select blocks

```{r select-blocks, include=FALSE}
# Number of selected blocks
n_blocks <- 2

# Set seed to make selection reproducible
set.seed(2017-08-07)

# Randomly select n_blocks
sjo_selected_blocks <- sjo_blocks %>%
  slice(
    sample(
      x = seq(from = 1, to = nrow(.), by = 1),
      size = n_blocks,
      replace = FALSE
    )
  )

# Save selected blocks as a shapefile
sjo_selected_blocks %>%
  st_write(
    "output/sjo_selected_blocks.shp",
    delete_dsn = TRUE
  )
```


Using the blocks shown in the previous map, `r n_blocks` where randomly selected
to define the home census area. Selected blocks are shown (in red) in the
following interactive map.

```{r plot-selected-blocks}
# Plot selected blocks
leaflet() %>%
  addTiles() %>%
  addPolygons(data = sjo_perimeter, color = "yellow") %>%
  addPolygons(data = sjo_blocks, color = "blue", opacity = 0.1) %>%
  addPolygons(data = sjo_selected_blocks, color = "red")
```


